I am writing to express my interest in the Senior Full Stack Developer position at Nuclear Promise X. With a background as a Senior Software Developer and a strong foundation in critical thinking, innovation, and problem-solving, I am excited about the opportunity to contribute to a more sustainable future.

I am a full-stack developer with a wide range of experience. I have around 8 years' experience developing in both front-end and back-end contexts, and am eager to shift focus to wherever the product needs are greatest. I have developed expertise in many different languages and frameworks. In my masters program, I was in the data system group with many people researching new AI techniques, but I have not had the opportunity to apply them. I am interested in learning how the field has progressed and working on AI solutions.

In my past, I built on top of legacy applications but recently was able to work on a greenfield project. I successfully led development of a new TypeScript Electron desktop application with a React front-end. In just 9 months, I was able to break down the requirements into small deliverables, resulting in a product allowing the company to reach customers with IP-sensitive models. I added a CI pipeline with playwright tests that enabled myself and another front-end developer to work quickly without regressions. My manager said it was a main contributor to delivering the application in a short timeframe and I began adopting it for other projects.

For all of my jobs, I have worked with JavaScript and TypeScript. In my recent role, I developed TypeScript expertise, resulting in open-source contributions to Electron and React-Toastify. Additionally, I worked with the larger team to implement a React design system that enabled consistent front-end experience across all products.

Outside of work, I have one major website that I built from scratch and have been continuously improving for the last 10 years. It is fun working with students running a large softball league and developing solutions to help them manage it. All the production costs are paid by the students, so I spend time optimizing performance to ensure site scales on affordable cloud platform tiers.

I look forward to the opportunity to discuss how my skills can contribute positively to innovative initiatives in the nuclear industry. Thank you for considering my application.