% Edit the following

% Personal information
\newcommand{\myname}{Dallas Fraser} % Your name (e.g. "John Smith")
\newcommand{\myemail}{dallas.fraser.waterloo@gmail.com} % Your email (e.g. "me@mydomain.com")
\newcommand{\myphone}{289-242-4248} % Your phone number (e.g. "123.456.7890")
\newcommand{\mylocation}{Port Elgin, ON} % Your general location (e.g. "PNW, USA")
\newcommand{\recipient}{Hiring Manager} % The recipient (e.g. "Hiring Manager")
\newcommand{\greeting}{Dear} % The greeting to use (e.g. "Dear")
\newcommand{\closer}{Kind Regards} % The closer to use (e.g. "Kind Regards")

% common paragraphs to use

\newcommand{\coverletterfrontendtesting}{
    In my past, I built on top of legacy applications but recently was able to work on a
greenfield project. I successfully led development of a new TypeScript Electron desktop ap
plication with a React front-end. In just 9 months, I was able to break down the requirements
into small deliverables, resulting in a product allowing the company to reach customers with
IP-sensitive models. I added a CI pipeline with playwright tests that enabled myself and
another front-end developer to work quickly without regressions. My manager said it was a
main contributor to delivering the application in a short timeframe and I began adopting it
for other projects.
}

\newcommand{\coverletteropensource}{
    I also have meaningful experience working with open-source projects. While upgrading
jQuery internally, I discovered a regression in the new version, traced it to the upstream
change, and submitted a pull request that addressed the issue. Since then, I’ve continued
contributing fixes for issues that directly impacted development, becoming comfortable with
different source-control workflows and CI environments across open-source communities.
}

\newcommand{\coverletteraccessibility}{
    I am a big advocate of end-to-end testing and 6 years ago attended a Cypress talk
about accessibility. In the talk I learned a lot about the benefits of accessibility, especially
when creating automated tests. Since then, I have made a conscious effort to expand the
accessibility of the products I work on. In my last role, I set up playwright scanning to
report WCAG violations to help other developers identify and correct issues
}

\newcommand{\coverlettercloudplatforms}{
    I have experience with all major cloud platforms like Azure, Google Cloud Product and Amazon Web
    Services. Most recently, I worked with AWS S3 to allow binary dependencies to be shared between
    cloud native  and off-line applications. I updated and maintained Docker images that
    were used in the Google Cloud.
}

\newcommand{\coverletterinformationretrieval}{
    During my master’s research at the University of Waterloo, I worked in information
retrieval with a focus on math search. My thesis explored how symbol layout trees and math
tokens could be integrated into traditional IR pipelines. I built a hybrid math IR system on
top of Lucene that indexed both structured math representations and textual content. The
system improved precision over its predecessors while simplifying the architecture, and it was
successfully used for the ARQMath tasks, outperforming other submissions. This work gave
me a deep understanding of retrieval models, indexing structures, and the design decisions
behind engines like Lucene and Elasticsearch
}

\newcommand{\coverletterdotnet}{
    I worked for 4 years in a company in the Microsoft ecosystem. The stack included C\#, .NET and Angular. I developed features with engineers from around the world and helped with a major migration of their front-end from AngularJs to Angular.
}